---
title: "Ring-Tailed Lemur Project"
output: html_document
---

```{r}
library(dplyr)
library(tidyverse)
```

### Importing My Data
```{r}
lemurs_full<- read.csv("RTL dataset.csv", header = TRUE) #full dataset
head(lemurs_full)

i <- sapply(lemurs_full, is.factor)
lemurs_full[i] <- lapply(lemurs_full[i], as.character)
lemurs_full %>% mutate_if(is.factor, as.character) -> lemurs_full

lemurs <- lemurs_full %>% select(Focal_ID, Point_Sample, Nearest_Neighbor, Point_Behavior, Behavior_Tally, Ad_Libitum, Contact_ID, X.1_ID, X.5_ID, X.10_ID) #only selecting the columns I'll need
head(lemurs)
```

### Creating data frames for each individual animal ID
```{r}
EV_full <- lemurs %>% filter(Focal_ID == "EV") 
KJ_full <- lemurs %>% filter(Focal_ID == "KJ")
MY_full <- lemurs %>% filter(Focal_ID == "MY") 
ZY_full <- lemurs %>% filter(Focal_ID == "ZY")
```

## Transforming and Unnestting Each Animal's Necessary Behavior Data

### Everest's Data
```{r}
EV_1<- EV_full %>% transform(Behavior_Tally = strsplit(Behavior_Tally, "/")) %>% unnest(Behavior_Tally,keep_empty=TRUE)
EV_1

EV_2<- EV_full %>% transform(Point_Behavior = strsplit(Point_Behavior, "/")) %>% unnest(Point_Behavior, keep_empty=TRUE)
EV_2

#don't need to do her ad_libitum data because all behavior entries were single entries
```

### King Julian's Data
```{r}
KJ_1<- KJ_full %>% transform(Behavior_Tally = strsplit(Behavior_Tally, "/")) %>% unnest(Behavior_Tally,keep_empty=TRUE)
KJ_1

KJ_2<- KJ_full %>% transform(Ad_Libitum = strsplit(Ad_Libitum, "/")) %>% unnest(Ad_Libitum, keep_empty=TRUE)

# don't need to do his point behavior data
```

### May's Data
```{r}
MY_1<- MY_full %>% transform(Behavior_Tally = strsplit(Behavior_Tally, "/")) %>% unnest(Behavior_Tally,keep_empty=TRUE)

MY_2<- MY_full %>% transform(Ad_Libitum = strsplit(Ad_Libitum, "/")) %>% unnest(Ad_Libitum, keep_empty=TRUE)

# don't need to do her point behavior data
```

### Zoey's Data
```{r}
ZY_1<- ZY_full %>% transform(Behavior_Tally = strsplit(Behavior_Tally, "/")) %>% unnest(Behavior_Tally,keep_empty=TRUE)

ZY_2<- ZY_full %>% transform(Point_Behavior = strsplit(Point_Behavior, "/")) %>% unnest(Point_Behavior, keep_empty=TRUE)

ZY_3<- ZY_full %>% transform(Ad_Libitum = strsplit(Ad_Libitum, "/")) %>% unnest(Ad_Libitum, keep_empty=TRUE)
```

# Greeting Behavior

### Everest greeting May
```{r}
EV_GT_MY_1<- EV_1 %>% filter(Behavior_Tally %in% c("GTA_MY","APA_MY")) #filtering out the greeting and approaching behaviors from Behavior_Tally column
EV_GT_MY_2<- EV_2 %>% filter(Point_Behavior == "GTA_MY") #filtering out the greeting and approaching behaviors from Point_Behavior column
EV_GT_MY_3<- KJ_2 %>% filter(Ad_Libitum == "EV_APA_MY")
EV_GT_MY_4<- ZY_3 %>% filter(Ad_Libitum %in% c("EV_GTA_MY", "EV_APA_MY"))
EV_GT_MY<- sum(nrow(EV_GT_MY_1),nrow(EV_GT_MY_2),nrow(EV_GT_MY_3),nrow(EV_GT_MY_4)) #adding up the number of rows from each for my final obj because I only care about how many times in total EV greeting MY
EV_GT_MY
```

### Everest greeting King Julian
```{r}
EV_GT_KJ_1<- EV_1 %>% filter(Behavior_Tally == "APA_KJ")
EV_GT_KJ<- nrow(EV_GT_KJ_1)
EV_GT_KJ
```

### Zoey greeting King Julian
```{r}
ZY_GT_KJ_1<- EV_1 %>% filter(Ad_Libitum == "ZY_GTA_KJ/")
ZY_GT_KJ_2<- ZY_1 %>% filter(Behavior_Tally == "GTA_KJ")
ZY_GT_KJ<- sum(nrow(ZY_GT_KJ_1),nrow(ZY_GT_KJ_2))
ZY_GT_KJ
```

### May greeting King Julian
```{r}
MY_GT_KJ_1<- EV_1 %>% filter(Ad_Libitum == "MY_GTA_KJ/")
MY_GT_KJ_2<- MY_1 %>% filter(Behavior_Tally == "APA_KJ")
MY_GT_KJ_3<- ZY_3 %>% filter(Ad_Libitum == "MY_GTA_KJ")
MY_GT_KJ<- sum(nrow(MY_GT_KJ_1),nrow(MY_GT_KJ_2),nrow(MY_GT_KJ_3))
MY_GT_KJ
```

### King Julian greeting Zoey
```{r}
KJ_GT_ZY_1<- KJ_1 %>% filter(Point_Behavior == "APA_ZY/")
KJ_GT_ZY_2<- MY_2 %>% filter(Ad_Libitum == "KJ_APA_ZY")
KJ_GT_ZY_3<- ZY_2 %>% filter(Point_Behavior == "APR_KJ")
KJ_GT_ZY<- sum(nrow(KJ_GT_ZY_1),nrow(KJ_GT_ZY_2),nrow(KJ_GT_ZY_3))
KJ_GT_ZY
```

### King Julian greeting Everest
```{r}
KJ_GT_EV_1<- KJ_1 %>% filter(Behavior_Tally == "APA_EV")
KJ_GT_EV_2<- EV_1 %>% filter(Behavior_Tally == "GTR_KJ")
KJ_GT_EV<- sum(nrow(KJ_GT_EV_1),nrow(KJ_GT_EV_2))
KJ_GT_EV
```

### Zoey greeting Everest
```{r}
ZY_GT_EV_1<- KJ_2 %>% filter(Ad_Libitum == "ZY_GTA_EV")
ZY_GT_EV_2<- ZY_1 %>% filter(Behavior_Tally == "APA_EV")
ZY_GT_EV<- sum(nrow(ZY_GT_EV_1),nrow(ZY_GT_EV_2))
ZY_GT_EV
```

### May greeting Zoey
```{r}
MY_GT_ZY_1<- KJ_2 %>% filter(Ad_Libitum == "MY_GTA_ZY")
MY_GT_ZY<- nrow(MY_GT_ZY_1)
MY_GT_ZY
```

### May greeting Everest
```{r}
MY_GT_EV_1<- KJ_2 %>% filter(Ad_Libitum == "MY_APA_EV")
MY_GT_EV_2<- MY_1 %>% filter(Behavior_Tally == "GTA_EV")
MY_GT_EV<- sum(nrow(MY_GT_EV_1),nrow(MY_GT_EV_2))
MY_GT_EV
```

### Zoey greeting May
```{r}
ZY_GT_MY_1<- ZY_1 %>% filter(Behavior_Tally %in% c("APA_MY","GTA_MY"))
ZY_GT_MY<- nrow(ZY_GT_MY_1)
ZY_GT_MY
```

### King Julian greeting May
```{r}
KJ_GT_MY_1<- KJ_1 %>% filter(Behavior_Tally %in% c("GTA_MY","APA_MY"))
KJ_GT_MY<- nrow(KJ_GT_MY_1)
KJ_GT_MY
```

### Creating a matrix to show the greeting behaviors
```{r}
GT_matrix<- matrix(c(0,1,8,0,2,0,3,4,3,2,0,1,3,3,2,0),nrow = 4, ncol = 4, byrow = T)
dimnames(GT_matrix)<- list(c("EV","KJ","MY","ZY"),c("EV","KJ","MY","ZY"))
GT_matrix
```

In this matrix actors are on the column on the left and receivers are on the row on top. Using greeting occurances as a determinant for dominance rank, we can assign the following rankings:
Everest greets May more than May greets Everest so MY = alpha female
King Julian greets Zoey the most so KJ = lowest ranking

### Creating a new dataframe 
```{r}
rank<- c(1,2,3,4)
ids<- c("MY","EV","ZY","KJ")
ranks<- data.frame(IDs=ids, Rank=rank)
summary(ranks)
ranks
```

# Grooming Behavior 

### Subordinates Grooming Dominants (includes any time a subordinate iniated a grooming bout or groomed a dominant individual unidirectionally)
```{r}
sub_gr_dom_1<- EV_1 %>% filter(Behavior_Tally %in% c("GRIA_MY","GRA_MY"))
sub_gr_dom_2<- MY_1 %>% filter(Behavior_Tally %in% c("GRIR_KJ","GRIR_EV"))
sub_gr_dom_3<- ZY_2 %>% filter(Point_Behavior == "GRIR_KJ")
sub_gr_dom_4<- ZY_1 %>% filter(Behavior_Tally == "GRIR_KJ")
sub_gr_dom_5<- ZY_3 %>% filter(Ad_Libitum %in% c("EV_GRIA_MY","EV_GRA_MY"))
sub_gr_dom<- sum(nrow(sub_gr_dom_1),nrow(sub_gr_dom_2),nrow(sub_gr_dom_3),nrow(sub_gr_dom_4),nrow(sub_gr_dom_5))
sub_gr_dom
```

### Dominants Grooming Subordinates (includes any time a dominant iniated a grooming bout or groomed a subordinant individual unidirectionally)
```{r}
dom_gr_sub_1<- KJ_2 %>% filter(Ad_Libitum %in% c("MY_GRIA_EV", "MY_GRA_EV"))
dom_gr_sub_2<- EV_1 %>% filter(Behavior_Tally == "GRIR_MY")
dom_gr_sub_3<- MY_1 %>% filter(Point_Behavior == "GRA_EV/" | Behavior_Tally == "GRIA_EV") #rememebr to add the / after the Point behavior here because we never unnessted it since they were all single behavior entries 
dom_gr_sub_4<- ZY_1 %>% filter(Behavior_Tally == "GRIA_KJ")
dom_gr_sub_5<- ZY_3 %>% filter(Ad_Libitum %in% c("MY_GRIA_EV","MY_GRA_EV"))
dom_gr_sub<- sum(nrow(dom_gr_sub_1),nrow(sub_gr_dom_2),nrow(sub_gr_dom_3),nrow(sub_gr_dom_4),nrow(sub_gr_dom_5))
dom_gr_sub
```

### Finding the percentage of times subordinates groom dominants and dominants groom subordinates
```{r}
sub_gr_dom_perc<- (sub_gr_dom/140)*100 # I'm dividing it by 140 because my raw data has a total of 14 focal observations with 10 point samples each focal observations
sub_gr_dom_perc

dom_gr_sub_perc<- (dom_gr_sub/140)*100
dom_gr_sub_perc

# Creating a data frame to show grooming order and percentage of grooming between subs and doms
percentage<- c(sub_gr_dom_perc,dom_gr_sub_perc)
grooming_order<- c("Subordinate to Dominant","Dominant to Subordinate")
gr_df<- data.frame("Grooming Order"=grooming_order, Percentage=percentage)
gr_df
```

```{r}
#install.packages("ggpubr")
library(ggpubr)
library(ggplot2)

plot<- ggboxplot(gr_df, x = "Grooming.Order", y = "Percentage", 
          color = "Grooming.Order", palette = c("#00AFBB", "#E7B800"),
          ylab = "Percentage of Occurences", xlab = "Grooming Order")
plot
```

### Running a binomal test for the grooming order data
```{r}
binom_test<- binom.test(c(sub_gr_dom,dom_gr_sub), p=0.5, conf.level = 0.95)
binom_test
```

There is no significant difference between the number of times subordinates iniated grooming/ groomed dominants and vice versa

```{r}
# Now doing the same thing but looking at the time subordinates ended grooming bouts with dominants
sub_gr_end_dom_1<- EV_1 %>% filter(Behavior_Tally == "GREA_MY")
sub_gr_end_dom_2<- MY_1 %>% filter(Behavior_Tally == "GRER_EV")
sub_gr_end_dom_3<- ZY_3 %>% filter(Ad_Libitum == "EV_GREA_MY")
sub_gr_end_dom<- sum(nrow(sub_gr_end_dom_1),nrow(sub_gr_end_dom_2),nrow(sub_gr_end_dom_3))
sub_gr_end_dom

# dominants ending grooming bouts with subordinates
dom_gr_end_sub_1<- KJ_2 %>% filter(Ad_Libitum == "MY_GREA_EV")
dom_gr_end_sub_2<- MY_1 %>% filter(Behavior_Tally == "GREA_KJ")
dom_gr_end_sub_3<- ZY_1 %>% filter(Behavior_Tally == "GREA_KJ")
dom_gr_end_sub<- sum(nrow(dom_gr_end_sub_1),nrow(dom_gr_end_sub_2),nrow(dom_gr_end_sub_3))
dom_gr_end_sub

end_binom_test<- binom.test(c(dom_gr_end_sub,sub_gr_end_dom), p=0.5, conf.level = 0.95)
end_binom_test
```

Also, no significant difference between the number of times subordinates ended grooming bouts with dominant inviduals and vice versa

## Mutual Grooming between pairs of individuals

### Everest and May
```{r}
EV_MY_GRM_1<- EV_2 %>% filter(Point_Behavior == "GRM_MY")
EV_MY_GRM_2<- EV_1 %>% filter(Behavior_Tally == "GRM_MY")
EV_MY_GRM_3<- ZY_3 %>% filter(Ad_Libitum %in% c("EV_GRM_MY","MY_GRM_EV"))
EV_MY_GRM<- sum(nrow(EV_MY_GRM_1),nrow(EV_MY_GRM_2),nrow(EV_MY_GRM_3))
EV_MY_GRM

EV_MY_GRM_perc<- EV_MY_GRM/140*100
EV_MY_GRM_perc
```

### May and King Julian
```{r}
MY_KJ_GRM_1<- MY_1 %>% filter(Point_Behavior == "GRM_KJ/" | Behavior_Tally == "GRM_KJ")
MY_KJ_GRM<- nrow(MY_KJ_GRM_1)
MY_KJ_GRM

MY_KJ_GRM_perc<- MY_KJ_GRM/140*100
MY_KJ_GRM_perc
```

### Zoey and King Julian
```{r}
ZY_KJ_GRM_1<- ZY_2 %>% filter(Point_Behavior == "GRM_KJ")
ZY_KJ_GRM_2<- ZY_1 %>% filter(Behavior_Tally == "GRM_KJ")
ZY_KJ_GRM<- sum(nrow(ZY_KJ_GRM_1),nrow(ZY_KJ_GRM_2))
ZY_KJ_GRM

ZY_KJ_GRM_perc<- ZY_KJ_GRM/140*100
ZY_KJ_GRM_perc
```

```{r}
GRM_percentage<- c(EV_MY_GRM_perc,MY_KJ_GRM_perc,ZY_KJ_GRM_perc)
GRM_pairs<- c("Everest & May", "May & King Julian","Zoey & King Julian")
GRM_df<- data.frame("Mutual Grooming Pairs"=GRM_pairs,"Percentage"=GRM_percentage)
GRM_df

```





# Some Location Behavior

### Looking at how many point samples each individual spent alone (contact Id = 0 and <1m = 0)
```{r}
EV_alone<- EV_1 %>% filter(Contact_ID == "" & X.1_ID == "")
EV_alone<- nrow(EV_alone)
EV_alone #number of point samples where EV was alone

EV_alone_perc<- EV_alone/140*100
EV_alone_perc #percentage of total point samples where EV was alone

# King Julian
KJ_alone<- KJ_1 %>% filter(Contact_ID == "" & X.1_ID == "")
KJ_alone<- nrow(KJ_alone)
KJ_alone

KJ_alone_perc<- KJ_alone/140*100
KJ_alone_perc

# May
MY_alone<- MY_1 %>% filter(Contact_ID == "" & X.1_ID == "")
MY_alone<- nrow(MY_alone)
MY_alone

MY_alone_perc<- MY_alone/140*100
MY_alone_perc

# Zoey
ZY_alone<- ZY_1 %>% filter(Contact_ID == "" & X.1_ID == "")
ZY_alone<- nrow(ZY_alone)
ZY_alone

ZY_alone_perc<- ZY_alone/140*100
ZY_alone_perc
```
### Adding new columns to my ranks df
```{r}
ranks$alone<- c(MY_alone,EV_alone,ZY_alone,KJ_alone) #creating a new columns for the number of point samples where each individual was alone 
alone<- ranks$alone

ranks$perc_alone<- c(MY_alone_perc,EV_alone_perc,ZY_alone_perc,KJ_alone_perc) #creating a new column for the percentage of total point samples where each individual was alone
perc_alone<- ranks$perc_alone
perc_alone

ranks
```

```{r} 
ranks$IDs <- as.character(ranks$IDs)
ranks$IDs <- factor(ranks$IDs, levels=c("MY", "EV", "ZY","KJ")) #I didn't want "IDs" to be listed alphabetically in the graph so first I switched it to a character list and then back to a factor list in the order I wanted

g<- ggplot(data=ranks, aes(x=IDs, y=perc_alone))
g<- g + geom_bar(stat= "identity")
g<- g + labs(x="Animal IDs", y= "Percentage of Point Samples Spent Alone")
g

```
Fig 1. The percentage of 2-min sample points in which no troop member was in contact or <1m away from the focal animal. Animals are arranged according to their designated ranking order in descending order from left to right. 



Trying out some nonparametric tests on my ranks vs perc_alone data
```{r}
# Kruskal Wallis Test - non parametric ANOVA

Krusk_test<-kruskal.test(data= ranks, perc_alone ~ IDs) #I feel like this test isn't applicable to my data because I don't have a range of perc_alone values for each ID, I just have one single value for each ID. By looking at the data, it seems like theres a pretty big difference between EV/MY and ZY/KJ but the test shows no significant difference across IDs 
Krusk_test

library(mblm) #needed for the nonparametric linear regression
library(psych) #needed for the correlation test

#This is the Spearman Correlation 

cor.test( ~ Rank + perc_alone,
         data=ranks,
         method = "spearman")

# This is the Kendall–Theil Sen Siegel nonparametric linear regression

model.k<- mblm(perc_alone ~ Rank, 
               data=ranks)
summary(model.k)



plot(perc_alone ~ Rank,
     data = ranks,
     pch  = 16)

abline(model.k,
       col="blue",
       lwd=2)
```

